Supplementary Information

### 2021-06-03 doc/manuscript/ForestGEO_treerings_SI.Rmd
added refs

A large recruitment pulse in the 1930s suggests that the site burned severely at that time, as would be consistent with a fire return interval of ~77 years in the Taiga Plains ecoregion (**REF**).

>>>>

A large recruitment pulse in the 1930s suggests that the site burned severely at that time, as would be consistent with a fire return interval of ~77 years in the Taiga Plains ecoregion [@johnstone_fire_2010; @walker_crossscale_2018].
